Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

%test
%=================================
%Yufei's stuff
%\usepackage{amsmath}
\usepackage{balance}
%\usepackage{times}
\usepackage{microtype}

@@

@@

\extraspacing {\bf Sets $\bm{R_1', R_2', ..., R'_{k-2}}$.} Fix any $i \in [k-2]$. For each rectangle $r \in R_i$, we compute four segments:
\myitems{
    \item $h_1$ (resp., $h_2$): the lowest (resp., highest) segment in $H$ that crosses $r$;

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment in $V$ that crosses $r$.
}
Define $r' = [x_1, x_2] \times [y_1, y_2]$, where $x_1$ (resp., $x_2$) is x-coordinate of $v_1$ (resp., $v_2$), and $y_1$ (resp., $y_2$) is y-coordinate of $h_1$ (resp., $h_2$). We say that $r'$ is the {\em trimmed rectangle} of $r$, and conversely, $r$ is the {\em full rectangle} of $r'$. Note that $r'$ exists if and only if $r$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$.

@@

@@

>>>>

%=================================
%Yufei's stuff
%\usepackage{amsmath}
\usepackage{balance}
%\usepackage{times}
\usepackage{microtype}

@@

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-b} & 
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-d} \\ 
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1'$ and $R_2'$ &
        \hspace{-4mm} (c) $R_1'$, $R_2'$, $H$, and $V$ &
        \hspace{-4mm} (d) $R_1^*$, $R_2^*$ ($= \emptyset$), $H$, and $V$
    \end{tabular}
    \figcapup 
    \caption{Finding H-V $k$-SJ result tuples of type 1 ($k = 4$)} 
    \label{fig:hv:type1:ex}
    \figcapdown 
\end{figure*}

@@

\extraspacing {\underline{\em Example.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2}$, $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following 4-tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_6)$. \qed

\extraspacing {\bf Sets $\bm{R_1', R_2', ..., R'_{k-2}}$.} Fix any $i \in [k-2]$. For each rectangle $r \in R_i$, we compute four segments:
\myitems{
    \item $h_\bot$ (resp., $h_\top$): the lowest (resp., highest) segment in $H$ that crosses $r$;

    \item $v_\vdash$ (resp., $v_\dashv$): the leftmost (resp., rightmost) segment in $V$ that crosses $r$.
}
Define $r' = [x_\vdash, x_\dashv] \times [y_\bot, y_\top]$, where $x_\vdash$ (resp., $x_\dashv$) is the x-coordinate of $v_\vdash$ (resp., $v_\dashv$), and $y_\bot$ (resp., $y_\top$) is the y-coordinate of $h_\bot$ (resp., $h_\top$). We say that $r'$ is the {\em trimmed rectangle} of $r$, and conversely, $r$ is the {\em full rectangle} of $r'$. Note that $r'$ exists if and only if $r$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$.

@@

\extraspacing {\underline{\em Example.}} Figure~\ref{fig:hv:type1:ex}b shows the rectangles in $R'_1 = \set{\alpha'}$ and $R'_2$ $=$ $\{\beta'_1,$ $\beta'_2\}$. For instance, $\alpha'$, which is trimmed from rectangle $\alpha$, is decided by $h_\bot$ $=$ $h_2$, $h_\top$ $=$ $h_6$, $v_\vdash = v_3$, and $v_\dashv = v_5$. The $(k-2)$-SJ on $R'_1$ and $R'_2$ returns $\J(R_1', R'_2, ..., R'_{k-2}) = \set{(\alpha', \beta_1'), (\alpha', \beta_2')}$.
\qed

%\yf{example}

@@

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1} &
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1} & 
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1} &
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1}
    \end{tabular}
\end{figure*}
